### 2018-03-16 paper/4-build.tex
Fix textif

When using a dirty bit, it is necessary to check all the dependencies of a key. For applicative build systems that list is simple to obtain, but for monadic build systems there is no general way to get all dependencies. Instead \Excel computes a \textit{static approximation} of the dependencies. For applicative rules that approximation is correct. For functions such as \textsf{IF} it marks the cell dirty if \textit{any} potential dependency has changed, even on the untaken \textif{if} branch. For functions such as \textsf{INDIRECT} whose dependencies cannot be guessed, it conservatively assumes the dependencies have always changed.

>>>>

When using a dirty bit, it is necessary to check all the dependencies of a key. For applicative build systems that list is simple to obtain, but for monadic build systems there is no general way to get all dependencies. Instead \Excel computes a \emph{static approximation} of the dependencies. For applicative rules that approximation is correct. For functions such as \cmd{IF} it marks the cell dirty if \emph{any} potential dependency has changed, even on the untaken \emph{if} branch. For functions such as \cmd{INDIRECT} whose dependencies cannot be guessed, it conservatively assumes the dependencies have always changed.
